\propertitle

### 2019-12-06 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-06T17:01:42+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The amount and degrees of the constraining moments depend on the questions
and hypotheses that a researcher is exploring. We give some examples in the
next two sections. Note that the constraint
equation~\eqref{eq:final_constraint} for the
distribution~\eqref{eq:app_maxent_pop_first} may not have exact solutions
if $N$ is strictly larger than $n$; and the possible discrepancy typically
increases with the number of constraints. This discrepancy comes from the
approximate character of two assumptions behind the maximum-entropy method
and of one assumption specific to our application: that the order of the
time bins is irrelevant, that measured averages equal expected values (or
equivalently, the number of time bins $T$ is infinite), and that an
activity level $\yA$ can equally likely be generated by any set of $\yA$
neurons in the larger population. The magnitude of this discrepancy can be
a signature of the (at least temporary) presence of a \enquote{neuronal
  assembly} \citep[\chap~12]{gerstneretal2014}{hebb1949_r2002}. We discuss
this matter in \sect~\ref{sec:assumptions}.

@@

\section{Assumptions and approximations}
\label{sec:assumptions}

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-06T17:16:23+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The amount and degrees of the constraining moments depend on the questions
and hypotheses that a researcher is exploring. We give some examples in the
next two sections. Note that the constraint
equation~\eqref{eq:final_constraint} for the
distribution~\eqref{eq:app_maxent_pop_first} may not have exact solutions
if $N$ is strictly larger than $n$; and the possible discrepancy typically
increases with the number of constraints. This discrepancy comes from the
approximate character of two assumptions behind the maximum-entropy method
and of one assumption specific to our application: that the order of the
time bins is irrelevant, that measured averages equal expected values (or
equivalently, the number of time bins $T$ is infinite), and that an
activity level $\yA$ can equally likely be generated by any set of $\yA$
neurons in the larger population. The magnitude of this discrepancy can be
a signature of the (at least temporary) presence of neuronal
\enquote{assemblies} or \enquote{clusters}
\citep[\chap~12]{gerstneretal2014}{hebb1949_r2002}. We discuss this matter
in \sect~\ref{sec:assumptions}.

@@

\section{The assumptions and approximations that define this model}
\label{sec:assumptions}
